\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-09 bare_conf.tex
bibliography fix.
bare_conf.tex
updated affiliation
bare_conf.tex
Darius Plikynas and acknowledgment is added

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Povilas Daniu\v{s}is\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania\\
Norwegian Centre for E-health Research\\
University Hospital of North Norway\\
Tromsø, Norway}}

@@

% use section* for acknowledgement
%\section*{Acknowledgment}
%The authors would like to thank...

@@

\begin{thebibliography}{1}
\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.

@@

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Povilas Daniu\v{s}is\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University,\\
Nature Research Center, Vilnius, Lithuania}

\and
\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania\\
Norwegian Centre for E-health Research\\
University Hospital of North Norway\\
Tromsø, Norway}

\and
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Darius Plikynas\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania}
}

@@

% use section* for acknowledgement
\section*{Acknowledgment}
This research is/was funded by the European Regional Development Fund according to the supported activity ‘Research Projects Implemented by World-class Researcher Groups’ under Measure No. 01.2.2-LMT-K-718.

%The authors would like to thank...

@@

\begin{thebibliography}{1}

@@

\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.
